---
title: "Write Up Linear Model with Prediction"
author: "Leonel D. Bautista"
date: "10/19/23"
output:
  html_document: default 
  pdf_document: default
---

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
install.packages("car")
require(car)

mydata <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)

```

# Introduction

($H_0$): There is no meaningful difference in how well arm strength, grip strength, or a combination of both can predict SIMS scores.

($H_A$): There is a noticeable difference in how well arm strength, grip strength, or a combination of both can predict SIMS scores. 

```{r}
model1 <- lm(SIMS~ARM,data=mydata)
plot(SIMS~ARM,data=mydata)
abline(model1)
specificdata1 <- data.frame(GRIP = 94, ARM = 88)
predict(model1, specificdata1, interval="prediction")
cor(mydata$SIMS, mydata$ARM)
```

The 95% prediction interval for estimating SIMS using ARM at the values GRIP=94 and ARM=88 is from -1.726209 to 3.138977. The overall prediction range is 4.865186. Among all the models, this has the second smallest prediction range, indicating it's the second most accurate predictor for SIMS at ARM = 88 and GRIP = 94.    

```{r}
model2 <- lm(SIMS~GRIP,data=mydata)
plot(SIMS~GRIP,data=mydata, main= "SIMS vs GRIP")
abline(model2)
specificdata2 <- data.frame(GRIP = 94, ARM = 88)
predict(model2, specificdata2, interval="prediction")
```


